Thread Pool in GeckoDB/BOLSTER

### 2018-07-12 Presentations/Milestone4/presentation.tex
Add some more summary to presentation 4

\begin{frame}
	\frametitle{Evaluation Setup}
	\begin{itemize}
		\item Tests run on different environments, including Windows 10, MacOS Sierra and Archlinux
		\item Presentation results measured on Archlinux with kernel 4.17.2-1 and 24 GB DDR4-SODIMM
		\item Each measure was repeated 3 times and an average value is used
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{Utilization of different slot distribution strategies}
	\begin{center}
		\includegraphics[width=0.8\textwidth]{img/slot_distr.png}
	\end{center}

\begin{frame}
	\frametitle{Utilization of lock-free vs mutex based heap}
	\begin{center}
		\includegraphics[width=0.8\textwidth]{img/lock_free.png}
	\end{center}

@@

\begin{frame}
	\frametitle{Summary}
	\begin{itemize}
		\item Better execution performance as baseline implementation
		\item Constant average waiting time over different pool sizes
		\item Small performance costs for enqueueing and waiting
	\end{itemize}
\end{frame}

\section{Conclusion}
	\begin{frame}
	\begin{center}
		\huge Conclusion
	\end{center}
\end{frame}

>>>>

\begin{frame}
	\frametitle{Evaluation Setup}
	\begin{itemize}
		\item Tests run on different environments, including Windows 10, MacOS High Sierra and Archlinux
		\item Presentation results measured on Archlinux with kernel 4.17.2-1 and 24 GB DDR4-SODIMM
		\item Each measure was repeated 3 times and an average value is used
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{Utilization of different slot distribution strategies}
	\begin{center}
		\includegraphics[width=0.8\textwidth]{img/slot_distr.png}
	\end{center}
	\begin{tabular}{c|c|c}
		\#Threads & distributed & compact \\
		1 & 0.998724 & 0.998787 \\
		2 & 0.935569 & 0.935331 \\
		3 & 0.917452 & 0.917384 \\
		4 & 0.918376 & 0.915736 \\
		5 & 0.795493 & 0.792239 \\
		6 & 0.906671 & 0.905388 \\
		7 & 0.818336 & 0.817147 \\
		8 & 0.774444 & 0.77419		
	\end{tabular}
\end{frame}

\begin{frame}
	\frametitle{Utilization of lock-free vs mutex based priority queue}
	\begin{center}
		\includegraphics[width=0.8\textwidth]{img/lock_free.png}
	\end{center}
\end{frame}

@@

\begin{frame}
	\frametitle{Summary}
	\textbf{Evaluation results:}
	\begin{itemize}
		\item Better execution performance as baseline implementation
		\item Constant average waiting time over different pool sizes
		\item Small performance costs for enqueueing and waiting
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Summary}
	\textbf{Project Evaluation:}
	\begin{itemize}
		\item All requirements of the thread pool fulfilled
		\item Compact but appropriate implementation feedback
		\item Literature research problematic 
		\begin{itemize}
			\item Few paper about thread pool implementations
			\item Focus on resizing
		\end{itemize}
	\end{itemize}
\end{frame}

%\section{Conclusion}
%	\begin{frame}
%	\begin{center}
%		\huge Conclusion
%	\end{center}
%\end{frame}
